Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-12 paper/structureScene.tex
move early int and late int description in section IV.B

A drawback of early integration is that it drastically reduces the number of training instances at the classifier stage, down to one per auditory scene.
In the context of the DCASE 2013 dataset, this corresponds to merely $8$ training instances per class, and $80$ instances overall, hence an increase in variance in statistical estimation and a risk of overfitting. \ja{That may be, but by averaging, we also reduce the variability of our data, which may be a good thing. If we're dealing with Gaussian processes, this is in fact a very good thing to do.}
On the contrary, a late integration scheme for $T=372\textrm{ ms}$ would yield $128$ instances per auditory scene \ja{How long is each recording? Should we specify this somewhere?}, resulting in $10240$ instances overall.
However, many of these instances may be silent or lack any salient properties of the class they are assigned to, hence an increase in bias and a risk of underfitting.
In short, early and late integration methods lie at opposite ends of the bias-versus-variance statistical tradeoff. We refer to \cite{Joder2009} for a comprehensive review of this problematic in the context of musical instrument recognition. \ja{Another important difference is that early integration makes the classifier objective more appropriate, since the SVM will maximize the final classification error on the training data, as opposed to some intermediate frame-level label.}

\subsection{Standardization}
\label{sec:stand}

@@

For ASSR, evaluation is performed on the private part of the DCASE2013 dataset. The metric used is the precision at rank $k$ ($p@k$), which is computed by taking a query item and counting the number of items of the same class within the $k$ closest neighbors, and then averagin over all query items. The $p@k$ is computed for $k=\{1,\ldots,9\}$, since each class only has $10$ items \ja{?}. Note that a $p@1$ is equivalent to the classification accuracy obtained by choosing the label of the closest neighbor for a given item. For each experimental setting, we only report the results obtained with the sets of parameters, \emph{i.e.} the number of clusters $m$ for the \emph{ob} approaches and the scaling parameter $N$ of the RBF kernels (see Eq. \ref{eq:kc}) leading to the best $p@9$. \ja{I'm not sure what this means. Do we fix $m$ and $N$ here for all experiments or do we optimize them over the test data each time? If so, this will bias the results, no?}

@@

The \emph{ob} approaches are compared to commonly used early integration approach (\emph{early}) for ASSR, while both early and late integration (\emph{late}) strategy are evaluated for the ASC setting (see Section \ref{sec:eili}). In this context early integration refers to an averaging of the features and late integration refers to a majority voting of the predictions. \ja{We should perhaps mention this in that particular section instead of over here.}

>>>>

A drawback of early integration is that it drastically reduces the number of training instances at the classifier stage, down to one per auditory scene.
In the context of the DCASE 2013 dataset, this corresponds to merely $8$ training instances per class, and $80$ instances overall, hence an increase in variance in statistical estimation and a risk of overfitting. \ja{That may be, but by averaging, we also reduce the variability of our data, which may be a good thing. If we're dealing with Gaussian processes, this is in fact a very good thing to do.}
On the contrary, a late integration scheme for $T=372\textrm{ ms}$ would yield $128$ instances per auditory scene \ja{How long is each recording? Should we specify this somewhere?}, resulting in $10240$ instances overall.
However, many of these instances may be silent or lack any salient properties of the class they are assigned to, hence an increase in bias and a risk of underfitting.
In short, early and late integration methods lie at opposite ends of the bias-versus-variance statistical tradeoff. We refer to \cite{Joder2009} for a comprehensive review of this problematic in the context of musical instrument recognition. \ja{Another important difference is that early integration makes the classifier objective more appropriate, since the SVM will maximize the final classification error on the training data, as opposed to some intermediate frame-level label.}
In the context of this paper, early integration refers to an averaging of the features and late integration refers to a majority voting of the predictions. 
%\ja{We should perhaps mention this in that particular section instead of over here.}
\subsection{Standardization}
\label{sec:stand}

@@

For ASSR, evaluation is performed on the private part of the DCASE2013 dataset. The metric used is the precision at rank $k$ ($p@k$), which is computed by taking a query item and counting the number of items of the same class within the $k$ closest neighbors, and then averaging over all query items. The $p@k$ is computed for $k=\{1,\ldots,9\}$, since each class only has $10$ items \ja{?}. Note that a $p@1$ is equivalent to the classification accuracy obtained by choosing the label of the closest neighbor for a given item. For each experimental setting, we only report the results obtained with the sets of parameters, \emph{i.e.} the number of clusters $m$ for the \emph{ob} approaches and the scaling parameter $N$ of the RBF kernels (see Eq. \ref{eq:kc}) leading to the best $p@9$. \ja{I'm not sure what this means. Do we fix $m$ and $N$ here for all experiments or do we optimize them over the test data each time? If so, this will bias the results, no?}

@@

The \emph{ob} approaches are compared to commonly used early integration approach (\emph{early}) for ASSR, while both early and late integration (\emph{late}) strategy are evaluated for the ASC setting (see Section \ref{sec:eili}).
